---
title: "Milestone Report"
author: "Koji"
date: "2018/7/25"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, message=FALSE}
library(stringr)
library(ggplot2)
library(dplyr)
library(quanteda)

set.seed(3301)
```

# Project Overview

Around the world, people are spending an increasing amount of time on their mobile devices for email, social networking, banking and a whole range of other activities. But typing on mobile devices can be a serious pain. SwiftKey, our corporate partner in this capstone, builds a smart keyboard that makes it easier for people to type on their mobile devices. One cornerstone of their smart keyboard is predictive text models. When someone types:

I went to the

the keyboard presents three options for what the next word might be. For example, the three words might be gym, store, restaurant. In this capstone you will work on understanding and building predictive text models like those used by SwiftKey.


_The motivation for this project is to:_

1. Demonstrate that you've downloaded the data and have successfully loaded it in.
2. Create a basic report of summary statistics about the data sets.
3. Report any interesting findings that you amassed so far.
4. Get feedback on your plans for creating a prediction algorithm and Shiny app.

_Review criteria_

1. Does the link lead to an HTML page describing the exploratory analysis of the training data set?
2. Has the data scientist done basic summaries of the three files? Word counts, line counts and basic data tables?
3. Has the data scientist made basic plots, such as histograms to illustrate features of the data?
4. Was the report written in a brief, concise style, in a way that a non-data scientist manager could appreciate?


# References
- [Data Science Specialization - Capstone | Community Site](http://datasciencespecialization.github.io/capstone/)
- [Quick Start Guide • quanteda](http://docs.quanteda.io/articles/pkgdown/quickstart.html)
